Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-09-11 paper/ifo-introduction.tex
re: re: restructuring introduction

In 2015, the first detection of gravitational waves from the merger of two black holes marked a breakthrough in modern astrophysics and revealed a new means to observe the universe~\cite{GW150914}.
This first observation and the many that followed it have led to increased public and media interest in gravitational-wave science. 
Gravitational-wave research groups around the world have produced demonstrations and activities to explain their research to general audiences. 
Activities range from hands-on demonstrations, exhibitions~\cite{TTExhibit:2020,LIGOScienceEducationCentre:online,GravityDiscoveryCentre:online}, and online data analysis tutorials~\cite{GWOSC:online,LOSC:2015}, to phone applications~\cite{LaserLabs:online,SciVR:online,chirp:online}, online games~\cite{BlackHoleHunter:online}, and musical performances~\cite{ArthurJeffesMusic:online,GravitySynthLeonTrimble:online}. %\han{look up Sarah Farmer's project}
% Here we describe the application of a table-top demonstration commonly used by gravitational-wave groups, to explain gravitational wave searches and signal processing analysis. 
%% We mention our experiment later, not here.

% What are gws and gw detectors 
Gravitational waves, predicted by Albert Einstein in his theory of general relativity~\cite{Einstein:1916}, are disturbances in spacetime caused by the acceleration of asymmetric massive objects.
The effect of gravitational waves is a change in lengths: a `stretching and squeezing' of the distance between objects. 
Ground-based gravitational-wave observatories such as the Advanced Laser Interferometer Gravitational-wave Observatory (aLIGO~\cite{AdvancedLIGO:2015}), Advanced Virgo~\cite{AdvancedVirgo:2015}, GEO600~\cite{GEO600:2010}, and KAGRA~\cite{KAGRA:2013} use the interference of laser light to measure changes in distance. 
Gravitational-wave observatories are extremely complex but are fundamentally based on the Michelson interferometer. 
Table-top interferometers are commonly used in undergraduate laboratory experiments~\cite{UgoliniEtAl:2019} and to demonstrate the science of gravitational wave detection to non-specialist audiences~\cite{ThorLabsIFO,NikhefIFO,AMIGO:online,TTExhibit:2020,LIGOIFOGlue,LIGOIFOMagnets}.

@@

In this paper, we present a table-top Michelson interferometer as a `toy' gravitational-wave detector designed to detect sound instead of gravitational waves. 
The demonstration can be used to teach topics ranging from continuous-wave detection and analysis to electronics, signal processing, and speech enhancement. 
%% I don't like the use of ``freedom to explore''.
Additionally, it allows students in courses such as physics and electrical engineering to explore the response of an accessible, yet nontrivial, opto-mechanical system using a hierarchy of data analysis techniques of increasing complexity, including those used in the search for continuous waves in LIGO and Virgo data~\cite{ScoX1O2Viterbi:2019, SuvorovaEtAl:2017,SuvorovaEtAl:2016}. 
This demonstration can be adapted to an effective outreach tool to explain gravitational wave science to a non-specialist audience.

>>>>

In 2015, the first detection of gravitational waves from the merger of two black holes marked a breakthrough in modern astrophysics and revealed a new means to observe the universe~\cite{GW150914}.
% What are gws and gw detectors 
Gravitational waves, predicted by Albert Einstein in his theory of general relativity~\cite{Einstein:1916}, are disturbances in spacetime caused by the acceleration of asymmetric massive objects.
The effect of gravitational waves is a change in lengths: a `stretching and squeezing' of the distance between objects. 
Ground-based gravitational-wave observatories such as the Advanced Laser Interferometer Gravitational-wave Observatory (aLIGO~\cite{AdvancedLIGO:2015}), Advanced Virgo~\cite{AdvancedVirgo:2015}, GEO600~\cite{GEO600:2010}, and KAGRA~\cite{KAGRA:2013} use the interference of laser light to measure changes in distance. 
Gravitational-wave observatories are extremely complex but are fundamentally based on the Michelson interferometer. 
Table-top interferometers are commonly used in undergraduate laboratory experiments~\cite{UgoliniEtAl:2019} and to demonstrate the science of gravitational wave detection to non-specialist audiences~\cite{ThorLabsIFO,NikhefIFO,AMIGO:online,TTExhibit:2020,LIGOIFOGlue,LIGOIFOMagnets}.

@@

In this paper, we present a table-top Michelson interferometer as a `toy' gravitational-wave detector designed to detect sound instead of gravitational waves. 
The demonstration can be used to teach topics ranging from continuous-wave detection and analysis to electronics, signal processing, and speech enhancement. 
%% I don't like the use of ``freedom to explore''.
Additionally, it allows students in courses such as physics and electrical engineering to explore the response of an accessible, yet nontrivial, opto-mechanical system using a hierarchy of data analysis techniques of increasing complexity, including those used in the search for continuous waves in LIGO and Virgo data~\cite{ScoX1O2Viterbi:2019, SuvorovaEtAl:2017,SuvorovaEtAl:2016}. 
% This demonstration can be adapted to an effective outreach tool to explain gravitational wave science to a non-specialist audience.
This demonstration also has the potential to be used as an outreach tool alongside other exhibitions~\cite{TTExhibit:2020,LIGOScienceEducationCentre:online,GravityDiscoveryCentre:online}, online data analysis tutorials~\cite{GWOSC:online,LOSC:2015}, phone applications~\cite{LaserLabs:online,SciVR:online,chirp:online}, online games~\cite{BlackHoleHunter:online}, and musical performances~\cite{ArthurJeffesMusic:online,GravitySynthLeonTrimble:online} which have been developed by gravitational wave research groups around the world. These tools allow scientists to cater to the increased public and media interest in this field and explain gravitational wave science to a non-specialist audience.
%\han{look up Sarah Farmer's project}
